%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Partner \& Customer Engineering VP} % Job title
    {Tapdata} % Organization
    {Shanghai, Shanghai} % Location
    {Mar.2022 - Sept.2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Still in landing stage mainly in charge of the entire customer engineering department} 
        \item {Trying to implement MEDDIC in Tapdata's sales organization}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consluting \& China South Region Rre-Sales Manager} % Job title
    {China Business Group, PingCAP} % Organization
    {Shenzhen, Guangdong} % Location
    {Aug. 2020 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Build a professional pre-sales team from 0 to 1 by hiring great people and giving them needed traning.}
        \item{Develop sales strategies with sales team based on regional customer portraits and segment characteristics to accomplish regional sales goals.}
        \item{Optimize and iterate best practices of the collaboration interface between pre-sales and sales side for decreasing resistance and improving human efficiency.}
        \item{Initiated, accelerated and deepened the use of TiDB as a technology in the financial industry in South China (China Merchants Bank, Guangfa Bank, Guangfa Securities, Anxin Securities, etc.) during the tenure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consluting \& Senior Solutions Architect } % Job title
    {China Business Group, PingCAP} % Organization
    {Shanghai, China} % Location
    {Dec. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyze and investigate possible solutions to meet the customer’s business and technical requirements.}
        \item {Collections of business/technical requirements through series of workshops with customers/stakeholders .}
        \item {Propose a batch system solution using TiSpark to meet BestPay's need}
        \item {Collaborate and occasionally lead field presales activities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Database Kernel Engineer \enskip|\enskip Tech Stack: Java, Scala, Spark, TiDB} % Job title
    {Real-time Analytics, PingCAP} % Organization
    {Shanghai, China} % Location
    {Dec. 2018 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Build TiSpark which served as a bride connecting TiDB ecosystem and Spark ecosystem from scratch}
        \item {Design and make TiSpark can directly insert into the underlying storage engine TiKV}
        \item {A go-to-person for any performance tunning and optimization of the TiSpark project}
        \item {github.com/pingcap/tispark}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Database Kernel Engineer \enskip|\enskip Tech Stack: Golang, Transaction, Raft, TiDB} % Job title
    {TiDB, PingCAP} % Organization
    {Shanghai, China} % Location
    {Dec. 2017 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Focus on SQL Parser, Optimizor, Execution and usability stuff.}
        \item {Have a solid understanding of Raft, Transaction, LSM-Tree.}
        \item {github.com/pingcap/tidb}
        \item {github.com/pingcap/tikv}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
