%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Projects}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    { Pre-Sales } % Role 
    {Gf Securities's Data as a Service Project} % Projects Name 
    {Shenzhen, Guangdong} % Location
    {Aug. 2020 - Dec. 2020} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Convery the TiDB technology in a narrative way to influential people inside the organization and change their mindset. }
        \item {Build the value pyramid via several Discovery Meetings in need to understand business as-is and to-be for answering why TiDB. }
        \item {Lead the Technical Feasibility Workshop and prioritize the current problem for answering why now and who anything. }
      \end{cvitems}
    }

\cventry
    { Pre-Sales } % Role 
    {Guangfa Bank's Business Middle Platform Project} % Projects Name 
    {Shenzhen, Guangdong} % Location
    {Aug. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepare a Competitive product analysis between TiDB and DRDS and persuade customer to give TiDB a chance.}
        \item {Lead the PoC session and beat the DRDS solution. }
        \item {Help the customer's engineer locating their code's bottleneck and improved the performance by 20\%. }
        \item {Feeds qualified and detailed info to the Sales to understand the bigger picture. }
      \end{cvitems}
    }

\cventry
    { Pre-Sales } % Role 
    {China Merchant Bank's Payments Record Project} % Projects Name 
    {Shenzhen, Guangdong} % Location
    {Dec. 2020 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepare detailed and convincible presentations resulting from thorough research trying to persuade them to choose TiDB while the engineering team already wants to move to MongoDB.}
        \item {Maintain close relationshop with crucial technical stakeholders in the organization. }
	\item {Plant idea or solution in favor to TiDB into technical stakeholders' mind.}
      \end{cvitems}
    }


%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------

\end{cventries}
