%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Projects}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    { Contrbutor \enskip | \enskip Tech Stack:Python} % Role 
    {Scikit learn, popular Python machine learning library(12.5k+ Github stars)} % Projects Name 
    {Minneapolis, Minnesota} % Location
    {Aug.2016 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed various pull requests for enhancements and bugfixes to the project. Servered as prolific reviewer of community-submitted pull requests. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    { Contrbutor \enskip | \enskip Tech Stack:Java, C++, Bash and Python} % Role 
    {Bazel, Google's own build tool} % Projects Name 
    {Minneapolis, Minnesota} % Location
    {Aug.2016 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed many bugfixes in bazel's building rules. Along with bug fixing, created and improved some white-box unit tests for bazel.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    { DEVELOPER \enskip | \enskip Tech Stack: java, Junit, Maven and Bash} % Role 
    {A simple MAP-REDUCE computing framework for more efficient data sorting} % Projects Name 
    {Minneapolis, Minnesota} % Location
    {Apr. 2016 - May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and Implemented a proactive fault tolerance protocol to prevent overall performace degradation due to computer node faults.}
        \item {Implemented a fault-injection protocol which is configurable at run time and allows the framework to inject faults at various probability to
increase the robustness of the designed fault tolerance protocol.}
        \item {Sorted 2GB of data in 10 minutes by using 10 computers that are communicating through TCP/IP.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DEVELOPER \enskip | \enskip Tech Stack: java, Junit, Maven and Bash} % Role 
    {A simple Distributed File System for more robust data storage} % Projects Name 
    {Minneapolis, Minnesota} % Location
    {Mar. 2016 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a distributed file system where multiple clients can execute different operations concurrently.}
        \item {Applied Quorum protocol served as replica control method to ensure transaction atomicity in case of network partitioning or crashing.}
        \item {Implemented the Synchronize operation to prevent stale file copies in different replicas.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {TEAM LEADER \enskip | \enskip Tech Stack: C++, Boost and cxxtest} % Role 
    {A mini PhotoShop for image processing} % Projects Name 
    {Minneapolis, Minnesota} % Location
    {Jan. 2016 - May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and developed a simplified PhotoShop software with support of both GUI and command line mode which possesses the same basic features as the full version of PhotoShop.}
        \item {Utilized various design patterns such as Factory, Singleton and Adaptor to optimize the overall performace of the software.}
      \end{cvitems}
    }

\end{cventries}
